Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-12 ms/main.tex
Add time figures to the notebook, add another figure to result 3

\begin{figure}[htb]
  \centering       
    \includegraphics[scale=0.5]{Result3_boundaries.pdf}
    \caption{\textbf{Evolution of cooperation under vertical, oblique and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red) and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is negative meaning $T_B>T_A$.
The vertical transmission rate $v$ is on the y-axis; the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are the solid and dashed lines. 
Here, $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$.}
    \label{fig:result3}
\end{figure}

>>>>

\begin{figure}[htb]
  \centering       
    \includegraphics[scale=0.5]{Result3_boundaries.pdf}
    \includegraphics[scale=0.5]{result3_positive_bias.pdf}
    \caption{\textbf{Evolution of cooperation under vertical, oblique and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
In (\textbf{a}) the horizontal bias $T_A-T_B$ is negative, in (\textbf{b}) the horizontal bias is positive.
The vertical transmission rate $v$ is on the x-axis; the cost boundaries $\hat\gamma_1$ and $\hat\gamma_2$ (\autoref{eq:cost_boundaries_v}) are the solid and dashed lines. 
In (\textbf{a}), $b=2$, $T_A=0.5$, $T_B = 0.7$, $\alpha = 0.7$ and (\textbf{b}) $b=1.2$, $T_A = 0.5$, $T_B = 0.4$, $\alpha = 0.4$.}
    \label{fig:result3}
\end{figure}
